---
title: "Homework 2"
author: "Bingkun Luo"
date: "9/26/2019"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
 
```

# Problem 1
## a
```{r}
Mr_Trash_Wheel_data = read_excel(path = "C:/Users/61693/Desktop/data Science/P8105_Hw2_bl2789/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
                        sheet = 1, range = "A2:N408") %>%

  janitor::clean_names()%>%
  drop_na(dumpster)

sports_balls_integer = as.integer(pull(Mr_Trash_Wheel_data,sports_balls))  
mutate(Mr_Trash_Wheel_data,sports_balls = sports_balls_integer)
```
## b
```{r}
precipitation_2018 = read_excel(path = "C:/Users/61693/Desktop/data Science/P8105_Hw2_bl2789/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
                        sheet = 5,range = "A2:B15") %>%
   janitor::clean_names()%>%
   drop_na(month)

precipitation_2018 = mutate(precipitation_2018,year = 2018)%>%
  select(year, precipitation_in_month = month,total)

```


```{r}
precipitation_2017 = read_excel(path = "C:/Users/61693/Desktop/data Science/P8105_Hw2_bl2789/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
                        sheet = 6,range = "A2:B15") %>%
   janitor::clean_names()%>%
   drop_na(month)

 precipitation_2017 = mutate(precipitation_2017,year = 2017)%>%
  select(year, precipitation_in_month = month,total) 
```

```{r}
##precipitation = rbind(precipitation_2017,precipitation_2018)

precipitation = full_join(precipitation_2017,precipitation_2018)
month_name = month.name[pull(precipitation,precipitation_in_month)]

Final_precipitation = mutate(precipitation, month_name)%>%
  select(year,month_name,total)

```
* The number of the observations in the **Mr.Trash Wheel** dataset is 334 and 14 variables and the key varibles are shown below.

* **Mr.Trash Wheel**
```{r echo=FALSE}
str(Mr_Trash_Wheel_data)
```
* The number of the observations in the **Final precipitation** dataset is 24 and 3 variables and the key varibles are shown below.

* **Final precipitation**
```{r echo=FALSE}
str(Final_precipitation)
```
* The total precipitation in 2018 is **`r sum(pull(precipitation_2018, total))`**
* The median number of sports balls in a dumpster in 2017 is **`r median(pull(Mr_Trash_Wheel_data[Mr_Trash_Wheel_data$year==2017,],sports_balls))`**

# Problem 2
## a
```{r}
pols_month = read_csv(file = "C:/Users/61693/Desktop/data Science/fivethirtyeight_datasets/pols-month.csv")%>% 
  separate(mon,into = c('year','month','day'),'-')%>% 
  mutate(month = month.name[as.integer(month)],
         president = recode(as.character(prez_gop),'1'='gop','0'='dem'))%>%
  select(-prez_dem,-prez_gop,-day)

```

## b
```{r}
snp = read_csv(file = "C:/Users/61693/Desktop/data Science/fivethirtyeight_datasets/snp.csv")%>% 
  separate(date,into = c('month','day','year'),'/')%>%
  mutate(month = month.name[as.integer(month)])%>%
  select('year','month','close')
```

## c
```{r}
unemployment = read_csv(file = "C:/Users/61693/Desktop/data Science/fivethirtyeight_datasets/unemployment.csv")

unemployment = pivot_longer(unemployment,
               Jan:Dec,
               names_to = 'month',
               values_to = 'unemployment')%>% 
   mutate(month = as.character(factor(month, labels = month.name)),
          year = as.character(Year))%>%
  select(year,month,unemployment)
  
```
## d
```{r}

Final = full_join(pols_month,snp)
Result = full_join(Final,unemployment)

str(Result)
```
* From table above, we can see that the **Result** dataset has `r nrow(Result)` observations and `r ncol(Result)` variables, including year, month, gov_gop, sen_gop, rep_gop, gov_dem, sen_dem, rep_dem, president, close, unemployment.

#Problem 3

```{r}
Popular_Baby_Names = read_csv(file = "C:/Users/61693/Desktop/data Science/P8105_Hw2_bl2789/Popular_Baby_Names.csv")

# Remove duplicate rows of the dataframe
Popular_Baby_Names = distinct(Popular_Baby_Names)
```

